---
title: Discrete Event Simulation - Part 1
author: Yunwei Hu
date: '2018-05-20'
slug: discrete-event-simulation-part-1
categories:
  - simulation
  - Reliability
tags:
  - DES
  - Repairable
  - python
  - rstats
---


# Discrete Event Simulation (DES) and Reliability Block Diagram (RBD)

DES is the simulation of stochastic processes with discrete state space, such as the classic M/M/1 queue: exponential interarrival and service times, with a single server. The state space can be defined as the queue length, which is integer-valued and thus “discrete.” This contrasts to, a continuous system, such as simulating a moving object, where state such as location is continuous.

System Reliability can be a DES problem, if we only consider discrete state of the components and not the continous parameters. The classic System Reliability theories are discrete state, and most of the time binary states. 

A reliability block diagram (RBD) is one of the frequently used tool for modeling system reliability. It use a block diagram method to show how component reliability contributes to the success or failure of a complex system. 

Commercial Reliability Software packages, such as Reliasoft Blocksim(R), use RBD to model the system and then use analytical or simulation methods to calculate the system reliability metrics. 

The RBD is a graphical interface to build the DES. However, Reliasoft Blocksim limits itself to the binary states. A more generic DES is desirable in certain complex systems. 

# DES in Python and R

DES are implemented in commercial software and also as generic framework in Java, Python, etc. SimPy is a process-based discrete-event simulation framework based on standard Python. More recenlty, Simmer is developed as a process-oriented and trajectory-based Discrete-Event Simulation (DES) package for R. It is designed to be a generic framework like SimPy or SimJulia, and it runs the DES with Rcpp to boost the performance and turning DES in R feasible. 

This post aims at evaluating Simpy and Simmer in the context of System Reliability. 

# Simpy + Reticulate

Reticulate package offers a set of tools for interoperability between Python and R. In this example, we use Reticulate to import a Simpy Model, and pass the simulation result to R as a data frame. 

## Machie Shop Example
### Prepare the python
```{r, message=FALSE}
library(tidyverse)
library(reticulate)
use_python("/Users/myhome/anaconda/bin/python")
source_python("simNHPP.py")
```

### The Simpy Code

See blow:
```
import random
import simpy
import pandas as pd

RANDOM_SEED = 42
MTTF = 100.0                     # Mean time to failure in minutes
REPAIR_TIME = 2.0               # Time it takes to repair a machine in minutes
NUM_MACHINES = 1                  # Number of machines in the machine shop
WEEKS = 4                         # Simulation time in weeks
SIM_TIME = WEEKS * 7 * 24 * 60    # Simulation time in minutes



def simNHPP(end_sim):
    event_log = []
    env = simpy.Environment()
    machine_1 = Machine(env, "Machine_1", event_log)
    machine_2 = Machine(env, "Machine_2", event_log)
    env.run(until = end_sim)
    event_log = pd.DataFrame(event_log, columns = ['event','time'])
    return event_log

def time_to_repair():
    """return time interval until the repair is done, and machine is ready to run again. """
    return REPAIR_TIME

def time_to_failure():
    """Return time until next failure for a machine.""" 
    return random.expovariate(1.0/MTTF)

# each machine has a name, and pass the event_log 
# time to failure and time to repair are defined globally. 
class Machine:
    def __init__(self, env, name, event_log):
        self.env = env
        self.name = str(name)
        self.work_proc = env.process(self.working(env, event_log))

    def working(self, env, event_log):
        while True:
            # Up until failure
            time_to_fail = time_to_failure()
            # print('%s: time to next failure is %.2f' % (self.name, time_to_fail))
            yield env.timeout(time_to_fail)

            # Repair for time_to_repair
            # print("%s Failure Starts at %.2f" % (self.name, env.now))
            event_log.append([self.name + " fails", env.now])
            repair_time = time_to_repair()
            yield env.timeout(repair_time)
            # print("%s is repaired at %.2f" % (self.name, env.now))
            event_log.append([self.name + " fixed", env.now])
```
### Simulation

```{r}
ptm <- proc.time()
ev <- 1:1000 %>% 
  map_df(function(x) cbind(simNHPP(SIM_TIME), tibble(n_run = x)))
map_time <- proc.time() - ptm
print(map_time)
head(ev)
```

# R-simmer

R-simmer has similar implentation as Simpy, but with Simmer, everything is monitored automatically, and reported in handy data frames. This works especially well when doing many replications.

## Prepare enviroment


```{r, message = FALSE}
library(tidyverse)
library(simmer)
library(simmer.plot)
```

## Define Machie

```{r}
machine <- function(mttf, repair_time, print_log = TRUE){
  if (print_log) {
      machie <- trajectory() %>% 
        set_attribute("n_fail", 0) %>% 
        timeout(function() rexp(1, 1/mttf)) %>% 
        log_("fail") %>% 
        set_attribute("n_fail", 1, mod="+") %>%
        seize("repairman") %>% 
        timeout(repair_time) %>% 
        release("repairman") %>% 
        log_("fixed") %>% 
        rollback(7)
  } else {
      machie <- trajectory() %>% 
        set_attribute("n_fail", 0) %>% 
        timeout(function() rexp(1, 1/mttf)) %>% 
        set_attribute("n_fail", 1, mod="+") %>%
        seize("repairman") %>% 
        timeout(repair_time) %>% 
        release("repairman") %>% 
        rollback(5)
    
  }

}
plot(machine(10,1))
```



```{r}
simmer_relia <- function(sim_time, print_log = T) {
  env <- simmer() %>% 
  # use resource to track system state
  # all items in series will require same "repair" resource. 
  # set capacity to inf, assuming no queue for repair
  # if repair resource busy -> system down
  # for n-oo-k items, if resource server > k-n ->system down 
  add_resource("repairman", capacity = Inf) %>% 
  add_generator("machine_a", machine(100, 1, print_log), at(0), mon = 2) %>% 
  add_generator("machine_b", machine(100, 1, print_log), at(0), mon = 2) %>% 
  run(sim_time)
  repair_log <- get_mon_resources(env)
}

```

Plot the repair_log
```{r}
# n_fail <- get_mon_attributes(env)
repair_log <- simmer_relia(100)
plot(repair_log, metric = "usage", "repairman", items = "server", steps = TRUE)
```

Calculate System Downtime, assuming in series.

```{r}

repair_log <- repair_log %>% 
  mutate(duration = c(diff(time),0)) %>% 
  # assuming series, any item down -> system down
  mutate(sys_state = if_else(server > 0, 0, 1) ) %>%
  dplyr::rename(state_start = time) 

downtime <- repair_log %>% 
  group_by(sys_state) %>% 
  summarise(duration = sum(duration)) 
print(downtime)
```

### loop

```{r}
ptm <- proc.time()
repair_log <- 1:1000 %>% 
  map_df(function(x) cbind(simmer_relia(SIM_TIME, F), tibble(n_run = x)))
simmer_time <- proc.time() - ptm
print(simmer_time)
tail(repair_log)
```

# Reference
Modarres, Mohammad; Mark Kaminskiy; Vasiliy Krivtsov (1999). Reliability Engineering and Risk Analysis. Ney York, NY: Marcel Decker, Inc. p. 198. ISBN 0-8247-2000-8.
